On Extending a Full-Sharing Multithreaded Tabling Design with Batched Scheduling

### 2015-06-01 paper.tex
paper -> revising (end)

This work is partially funded by project SIBILA
(NORTE-07-0124-FEDER-000059) under the North Portugal Regional
Operational Programme (ON.2 – O Novo Norte) and under the National
Strategic Reference Framework (NSRF), through the European Regional
Development Fund (ERDF) and, by national funds, through the Portuguese
Foundation for Science and Technology (FCT).

>>>>

This work is partially funded by the North Portugal Regional
Operational Programme (ON.2 – O Novo Norte) and by the National
Strategic Reference Framework (NSRF), through the European Regional
Development Fund (ERDF) and the Portuguese Foundation for Science and
Technology (FCT), within projects NORTE-07-0124-FEDER-000059 and
UID/EEA/50014/2013.
